\chapter{Work Packages and Timeline}
\label{chap:wps}
In this section, we define the work packages and timeline to fulfill the specified tasks in the following months.

\section{Work Packages}
We divide our thesis into Work packages (WP) or Tasks.
We can use this to track the progress of the thesis and get feedback.

\paragraph{WP1 (Introduction):} In this package, we would like to start by introducing the topic, identifying the problems by defining the problem statement, and finally, defining our research and solution approach.
\begin{enumerate}
    \item Motivation
    \item Problem Statement
    \item Research and Solution Approach
\end{enumerate}

\paragraph{WP2 (Foundation):} In this package, we would like to define some terminologies according to the research (e.g., Continous Experimentation, Low-Code, etc.)

\paragraph{WP3 (Related Work):} Here, we would like to find some State-of-the-art research and compare them with the research questions or requirements we define for the thesis.
\begin{enumerate}
    \item State-of-the-art research
    \item Comparison
\end{enumerate}

\paragraph{WP4 (Design Science Research):} Here, we explain our research approach and the DSR in depth.
	\begin{itemize}
		\item DSR Method and Process
		\item Design Principles (DP): We define various DPs from literature reviews on lean development, UI prototyping, etc.
		\item Design Features (DF)
	\end{itemize}

\paragraph{WP5 (Design):} Here, we would like to design our tool as per the LEAN development cycle, containing the Build, Measure, and Learn phases.
\begin{enumerate}
    \item Build: We would like to build the tool for the designers so that they can create prototypes and experiment with the users.
    \item Measure: In this step, we would assign the experiment variants and assign tasks to the users to measure their feedback.
    \item Learn: Finally, we would learn from the experiment by analyzing and improving the prototype. This finishes one cycle iteration, and the designers repeat the steps with the updated prototype.
\end{enumerate}

\paragraph{WP6 (Implementation):} In this package, we would like to implement the prototypes by developing the meta-models, defining the architectures, and coding them for visualization of the prototypes.
\begin{enumerate}
    \item Architecture: We would define the architecture for the experimentation server (containing experimentation and task manager) and the prototypes (containing prototype manager)
    \item Technologies used: Here, we define the technologies that we use for the implementation of the platform 
    \item Demonstration: Developing, Testing, and Deployment of the application (using docker\footnote{Docker: \url{https://www.docker.com/}})
\end{enumerate}

\paragraph{WP7 (Evaluation):} In this package, we would test our prototypes by creating the experiments and the tasks for the users and measuring feedback from them.
\begin{enumerate}
    \item Create a user case study and assign experiments and tasks to the users 
    \item Analyze the measurements
    \item Limitations and Risks
\end{enumerate}

\paragraph{WP8 (Conclusion):} Here, we conclude the thesis and write the scope for future work.
\begin{enumerate}
    \item Conclusion
    \item Future work
\end{enumerate}

\input{chapters/ma-ganttchart}