% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      


Writing a master's thesis and conducting research is a challenging journey that cannot be accomplished without the support of many people. 
I want to express my gratitude to everyone who has supported me throughout the journey of completing the master's thesis.

Firstly, I thank \textit{Dr. Sebastian Gottschalk} for his immense support throughout my thesis. 
He was always available to provide a solution to every problem that I encountered and helped me to finish my thesis smoothly.
Under his mentorship, I gained a deeper knowledge of software engineering, and his constant encouragement piqued my interest in exploring new research directions. 
I am truly grateful for his invaluable contributions to my professional growth and academic journey.
His expertise in software engineering has been instrumental in shaping my ideas and improving the quality of my thesis. 
His inputs and suggestions were valuable in making the thesis more comprehensive and relevant.
Secondly, I would like to thank \textit{Dr. Enes Yigitbas}, my first supervisor, for his unwavering support and guidance throughout the thesis. 
He was always available to help and provided valuable insights, especially during the user study conducted for evaluating the thesis. 
He also encouraged his students to participate in my user study, which helped me gather more data.
Next, I want to express my sincere appreciation to \ac{sicp} for providing me with the necessary resources and space to conduct my research.
I am also thankful to all the participants who participated in the user study and provided valuable feedback for evaluating the proposed approach. Without their participation, this thesis would not have been possible.

Lastly, I would like to express my heartfelt gratitude to my parents, dad \textit{Shivananda} and mom \textit{Radhika}, and my brother \textit{Rohit} for their relentless support and motivation throughout my master's studies. 
Their constant love, motivation, and guidance helped me overcome the challenges I encountered during my research. 
Moreover, I am grateful for the support from my friends here in Germany, who invited me to celebrate different festivals and other fun activities, helping me feel at home.
Last but not least, I thank all my friends back in India for their support and encouragement.
\end{acknowledgements}